%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Kai Thompson} \\ \vspace{1pt}
    \textit{\large 458 Richmond St W, Toronto, ON} \\ \vspace{1pt}
    \href{tel:+19054679086}{\underline{(905) 467-9086}} $|$ \href{mailto:kai.thompsonaz@gmail.com}{\underline{kai.thompsonaz@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/kai-thompson-12aa13181/}{\underline{linkedin.com/in/kai-thompson}} $|$
    \href{https://github.com/kai-thompson}{\underline{github.com/kai-thompson}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{Jan. 2022 -- Present}
      {Newton.co}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Contributed to the development of a deposit/withdrawal microservice, which handles over 1 billion CAD in transactions annually, by writing a majority of the tests and implementing failsafes.}
        \resumeItem{Implemented a microservice that greatly improved the efficiency of generating monthly crypto balance reports, reducing the time by 22000x.}
        \resumeItem{Designed and developed a ledger database for tracking user balances and trades, used to ensure accurate state.}
        \resumeItem{Deployed a blockchain reconciliation microservice to validate on-chain deposits and withdrawals, ensuring the security and integrity of all transactions.}
        \resumeItem{Worked on adding new and experimental features to our React Native mobile application.}
      \resumeItemListEnd

    \resumeSubheading
      {Frontend Developer}{Nov. 2021 -- Jan. 2022}
      {Treasure Chess}{Remote}
      \resumeItemListStart
        \resumeItem{As a core team member, played a key role in the development of the user interface of chess.com's NFT collectible marketplace, specifically focusing on front-end contributions.}
        \resumeItem{Designed and implemented scalable React components, styled using TailwindCSS, and thoroughly tested using Storybook to ensure a seamless user experience.}
        \resumeItem{Built and implemented marketplace sorting and filtering functionality using a GraphQL API, allowing for dynamic and efficient data retrieval.}
        \resumeItem{Developed and integrated functionality to seamlessly cover users' blockchain transaction fees, ensuring a smooth and streamlined marketplace experience.}
        \resumeItem{Utilized React Spring to bring dynamic features and animations to the marketplace, making it more interactive and engaging for users.}
    \resumeItemListEnd

    \resumeSubheading
      {Founder}{Oct. 2020 -- Aug. 2021}
      {Krypto Depot}{Burlington, ON}
      \resumeItemListStart
        \resumeItem{Trading desk totalled over 1800 sales, averaging CAD 2000 each.}
        \resumeItem{I implemented precautions including AML(anti-money laundering) compliance and FINTRAC reporting.}
        \resumeItem{Received 100\% positive feedback from 131 reviews.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/kai-thompson/i-can-react}{\underline{i-can-react}} $|$ \emph{Typescript, React, Tailwind CSS, Redux, Vite}}{November 2022}
          \resumeItemListStart
            \resumeItem{Created a React boilerplate to quickly start new projects.}
            \resumeItem{Utilized Tailwind CSS to create a custom theme and components.}
            \resumeItem{Implemented Redux Tool Kit (RTK) to manage state across the application.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/kai-thompson/eth-date-to-block}{\underline{eth-date-to-block}} $|$ \emph{Typescript, Jest, NPM, GitHub Workflows}}{October 2022}
          \resumeItemListStart
            \resumeItem{Developed a NPM package to efficiently convert a date to a block number.}
            \resumeItem{2x faster and 73x smaller than the leading solution by implementing an interpolation search algorithm.}
            \resumeItem{In October 2022, it reached a peak of 292 weekly downloads.}
            \resumeItem{Utilized GitHub Workflows to automate testing and publishing to NPM.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Typescript, Javascript, Golang, Python, Swift, HTML/CSS, SQL (Postgres), GraphQL, Solidity} \\
     \textbf{Frameworks}{: React, React Native, Node.js, Express.js, Next.js, Django, Gorilla, MongoDB/RealmDB} \\
     \textbf{Libraries}{: Redux, TailwindCSS, SASS, Vite, NumPy, Pandas, Jest, Puppeteer} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, VS Code, Eclipse, Postman} \\
    }}
 \end{itemize}


 %-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Chainshot}{Remote}
    {Ethereum and Javascript Developer Bootcamp}{Oct. 2021 -- Dec. 2021}
  \resumeSubheading
    {Nelson High School}{Burlington, ON}
    {Highschool Diploma; 4.00 GPA}{Sept. 2016 -- June 2021}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}